Printing in a Periphery: a Quantitative Study of Finnish Knowledge Production, 1640-1828

### 2017-02-02 inst/examples/20170201-manuscript.Rmd
analysis fix

```{r 201606krakow-init2, echo=FALSE, message=FALSE, warning=FALSE, echo=FALSE, cache=TRUE}
# Full combined catalogue (Fen + Kun) with marked duplicates
df.combined.preprocessed <- readRDS("df.combined.Rds")
# Data with duplicates removed
df.full <- df.combined.preprocessed %>% filter(!remove)
# Data with years limited as well
df0 <- df.full %>% filter(publication_year >= min.year & publication_year <= max.year)
```

@@

# Take cities from Fennica for Turku
cat <- "Kungliga"
df2 <- df0 %>% filter(publication_place %in% "Turku") %>%
      	      filter(catalog == cat) %>%
              filter(publication_decade %in% pop$publication_decade) %>%
	      select(publication_decade, publication_place) %>%	      
	      group_by(publication_decade, publication_place) %>%
	      summarise(n = n())

@@

# Take cities from Fennica for Turku
cat <- "Kungliga"
df2 <- df0 %>% filter(publication_place %in% "Turku") %>%
      	      filter(catalog == cat) %>%
	      group_by(publication_year, publication_place) %>%
	      summarise(n = n(), paper = sum(paper, na.rm = TRUE))

@@

dfs <- filter(df, gatherings == "8vo")
p <- ggplot(df, aes(x = publication_year, y = paper)) +
       geom_line(aes(color = publication_place), size = 1) +
       geom_point(aes(color = publication_place), size = 2) +
       xlab("Publication year") +
       ylab("Paper (sheets)") +
       ggtitle("Paper consumption in selected cities") +
       guides(color = guide_legend(title = "Place", reverse = TRUE))
print(p)

@@

df$title_length <- nchar(df$title)
dfs <- df %>% group_by(publication_year) %>%
              summarise(mean_title_length = mean(title_length, na.rm = TRUE))

>>>>

```{r 201606krakow-init2, echo=FALSE, message=FALSE, warning=FALSE, echo=FALSE, cache=TRUE}
# Full combined catalogue (Fen + Kun) with marked duplicates
df.combined.preprocessed <- readRDS("df.combined.Rds")
# Data with duplicates removed
df.full <- df.combined.preprocessed %>% filter(!remove)
# Data with years limited as well
df0 <- df.full %>% filter(publication_year >= min.year & publication_year <= max.year)
df0$title_length <- nchar(df0$title)
```

@@

# Take cities from Fennica for Turku
cat <- "Fennica"
df2 <- df0 %>% filter(publication_place %in% "Turku") %>%
      	      filter(catalog == cat) %>%
              filter(publication_decade %in% pop$publication_decade) %>%
	      select(publication_decade, publication_place) %>%	      
	      group_by(publication_decade, publication_place) %>%
	      summarise(n = n())

@@

# Take cities from Fennica for Turku
cat <- "Fennica"
df2 <- df0 %>% filter(publication_place %in% "Turku") %>%
      	      filter(catalog == cat) %>%
	      group_by(publication_year, publication_place) %>%
	      summarise(n = n(), paper = sum(paper, na.rm = TRUE))

@@

# Take cities from Kungliga except Turku
cat <- "Kungliga"
df1 <- df0 %>% filter(publication_place %in% setdiff(cities, "Turku")) %>%
      	       filter(catalog == cat & gatherings == "8vo") %>%
	       group_by(publication_year, publication_place) %>%
	       summarise(n = n(), paper = sum(paper, na.rm = TRUE))

# Take cities from Fennica for Turku
cat <- "Fennica"
df2 <- df0 %>% filter(publication_place %in% "Turku") %>%
      	       filter(catalog == cat & gatherings == "8vo") %>%
	       group_by(publication_year, publication_place) %>%
	       summarise(n = n(), paper = sum(paper, na.rm = TRUE))

p <- ggplot(df, aes(x = publication_year, y = paper)) +
       geom_line(aes(color = publication_place), size = 1) +
       geom_point(aes(color = publication_place), size = 2) +
       xlab("Publication year") +
       ylab("Paper (sheets)") +
       ggtitle("Paper consumption in selected cities") +
       guides(color = guide_legend(title = "Place", reverse = TRUE))
print(p)

# -----------------------------------------

@@

dfs <- df %>% group_by(publication_year) %>%
              summarise(mean_title_length = mean(title_length, na.rm = TRUE))
